Demo for IEEE Journals

### 2020-02-19 Paper.tex
Structure Update

\section{Application Domain}
Paragraph one Paragraph one Paragraph one Paragraph one Paragraph one 
Paragraph one Paragraph one Paragraph one Paragraph one Paragraph one 
Paragraph one Paragraph one Paragraph one Paragraph one Paragraph one 
Paragraph one Paragraph one Paragraph one Paragraph one Paragraph one 
Paragraph one Paragraph one Paragraph one Paragraph one Paragraph one

@@

@@

>>>>

@@

\subsection{Hardware}

@@

\subsection{Network}

\subsection{Internet Data Flow}

udbcsiuhcbaiuejwndfciujwds

\subsection{Application Layer}

\subsubsection{Cloud Computing and Database}

\subsubsection{Other Concerns}
